---
title: "Lab 9 Intro"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Seating
1. If you already have a group, it will be helpful to start sitting next to each other.
2. If you don't have a group, hang tight we are working on it.
3. Please setup your computer as normal for today.

## Warm-up
```{r}
library(tidyverse)
library(janitor)
```

1. In the data folder there is an epidemiology data set on an outbreak of malaria.
```{r}
malaria<-read_csv("data/malaria.csv")
malaria
```

2. `rdt` refers to rapid diagnostic test and they are identified here by age group.
3. Make the data tidy and store them as a new object.


```{r}
malaria_age<-malaria %>% 
  pivot_longer(`malaria_rdt_0-4`:malaria_rdt_15,
               names_to="age",
               values_to="malaria_rdt")
malaria_age
```

4. Which district had the highest *total* number of cases on July 30, 2020?
```{r}
malaria %>% 
  filter(data_date=="2020-07-30") %>% 
  group_by(District) %>% 
  summarize("total_district_cases"=sum(malaria_tot,na.rm=T)) %>% 
  arrange(desc(total_district_cases)) %>% 
  head(n=4)
```

