---
title: "Lab 4 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Setup
1. Login to the lab computer (please don't use your personal computer).  
2. Navigate to github.com and login.   
2. Copy your repository to the desktop.   
5. Copy the class repository to the desktop (https://github.com/jmledford3115/datascibiol).  
6. Copy the files for today's lab from the class repository and paste them into **your** repository.  
7. Open today's lab in RStudio.  

## Review from last time
### *With a partner, discuss the following questions*
1. How is a data frame and how is it different than a data matrix?  
A data frame will show you columns and rows and tell you the classes of the data underneath the name of the column. Also the data matrix can have names for rows whereas data frames don't have names for rows.

2. What is the command we use to import .csv files into R?  
```{r}
#data name <-readr::read_csv(#exact name of file in the working directory)
```

3. Take a moment to show your repository on GitHub to a partner. Can you make any improvements?  
I could probably put all the labs in a folder called "Labs"

## Warm-up
1. In a new R Markdown document, load the tidyverse and a package called `palmerpenguins`.
2. What are the dimensions of the dataset `penguins`?
3. What are the names of the variables in the `penguins` dataset?
4. How many individuals were sampled on each island in the `penguins` dataset?
5. What is the mean body mass for all individuals in the `penguins` dataset?
