---
title: "Lab 6 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Setup
1. Login to the lab computer (please don't use your personal computer).  
2. Navigate to github.com and login.   
2. Use GitHub desktop to clone your repository to the desktop.   
5. Copy the class repository to the desktop (https://github.com/jmledford3115/datascibiol).  
6. Copy the files for today's lab from the class repository and paste them into **your** repository.  
7. Open today's lab in RStudio.  

```{r}
library(tidyverse)
library(janitor)
```


## Review from last time
### *With a partner, discuss the following questions*
1. What is a pipe? Why are they useful in R?
A pipe is a way of inserting the results of a function into another function. They are useful because now you can do more than one function in a coding block and multiple funcitons in a row.
2. What is the shortcut for making a pipe?
Command+Shift+M
3. What is the difference between `select`, `filter`, and `mutate`?
select picks out certain columns. filter picks out certain rows. mutate adds a new columns based on previous, already-existing columns.
4. What are the logistics of midterm 1?
50 mins solo turn in for 5 points, 50 mins duo for group work.
### Warm-up
1. Open the data `ecs21351-sup-0003-SupplementS1.csv`
#We skipped the first two rows of the data
```{r}
ecosphere<-readr::read_csv("data/ecs21351-sup-0003-SupplementS1.csv",skip=2)
```
2. Clean the names of the variables
```{r}
names(ecosphere)
```
```{r}
ecosphere <- janitor::clean_names(ecosphere)
```

3. Explore the data using a function of your choice
```{r}
glimpse(ecosphere)
```

4. Are there more veggie, omni, insecivore, or nectar feeders in the data?
```{r}
table(ecosphere$diet)


tabyl(ecosphere$diet)
```
There are in the diet column of the data.
5. Which families are Veggie?
```{r}
ecosphere %>% 
  select(family,diet) %>% 
  filter(diet=="Vegetation")
```
Anatidae,Phasianidae,Tetradonidae,and Rallidae are families that are veggie eaters.
